\documentclass[12pt,a4paper,oneside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx, titlesec}
\usepackage{hyperref}
\usepackage{url}
\usepackage{cite}
\titleformat{\chapter}
	{\normalfont\Large\bfseries}{\thechapter.}{1em}{}
\graphicspath{ {images/} }

\newcommand{\appname}{ablubb}
\newcommand{\blubb}{blubb}
\newcommand{\beapDB}{beapDB}
\newcommand{\beapServer}{beap server}

\begin{document}

\bibliographystyle{ieeetr}
%\citep{}, \citet{}, \citep*{}
\title{
	{\huge \appname{} documentation}
	{\\ \large Hochschule Heilbronn}
}
\author{Benjamin Richter}
\date{\today}
\maketitle
\tableofcontents

\chapter{Introduction}

\section{Project description}

\section{Project management and communication}
%comment
project management \cite{mihaela2013measurement}. 


\section{General goals}


\chapter{Execution}

\section{Backlog}

\begin{itemize}
     \item As a User, I don't want a message I wrote but did not send to disappear.
     \item As a User, I want to shut down the application. 
     \item As a User, I want to choose my own password. 
     \item As a Admin, I want to open a new Admin thread.
     \item As a Manager, I want to open a new Management thread. 
     \item As a Manager, I want to show a TASK only to some Users. 
     \item As a User, I want to finish a TASK (mark it as finished). 
     \item As a User, I want to take a TASK.
     \item As a User, I want to view only TASKS from a thread or all threads.
     \item As a Manager, I want to post TASKS User can work on. 
     \item As a User, I want to view only QUESTIONS from a thread or from all threads. 
     \item As a User, I want to ask some other User a QUESTION and view the results as a chart. 
     \item As a User, I want to edit my own profile description. 
     \item As a User, I want to see profiles of others with description, status, profile picture and batches he/she earned.
     \item As a User, I want to earn rewards/batches for my engagement within Blubb.
     \item As a User, I want to edit my "thread profiles".
     \item As a User, I want to switch off notifications on my mobile.
     \item As a User, I want to change my profile picture by uploading another one.
     \item As a User, I want to change how often my mobile pulls new messages.
     \item As a User, I want to show others what I'm doing right now via some kind of "status".
     \item As a User, I want to have a profile picture which is shown with my messages.
     \item As an Admin, I want to reset a Users password when he/she forgot her password.
     \item As an Admin, I want to delete a thread from an User.
     \item As an Admin, I want to delete messages from an User.
     \item As a User, I want to have some kind of link to quoted messages so that I can read immediately what has been quoted.
     \item As a User, I want to quote another message.
     \item As a User, I want to hide different threads on my mobile and on the web front end. For this I want some kind of profiles where I can manage which thread to hide.
     \item As a User, I want to hide messages from threads so I don't have to read all the messages from e.g. the coffee break thread.
     \item As a User, I want to search for a word within a single thread.
     \item As a User, I want to search for a word and expect to see all messages from all threads containing this word, sorted chronological.
     \item As a User, I want to view my "like Count" for a period of time, e.g. last week.
     \item As a User, I want to view my "like Count" so I can see how many likes I've got for all my messages.
     \item As a User, I want to be able to "like" a good message.
     \item As a User, I want to share an audio file.
     \item As a User, I want to upload an audio-file.
     \item As a User, I want to view a uploaded/shared video within a message.
     \item As a User, I want to see uploaded/shared pictures within the message.
     \item As a User, I want to share a video in a thread.
     \item As a User, I want to upload a video to a message I'm writing.
     \item As a User, I want to share a picture in a thread by using the Share Button from Android and be able to write some text to this.
     \item As a User, I want to upload a picture to a message I'm writing.
     \item As a User, I want to change a message I wrote.
     \item As a User, I want to delete a message I wrote and nobody can read it anymore or reply to it. 
     \item As a User, I want to add descriptions to my threads.
     \item As a User, I want to open a new thread to talk with others about a specific topic.
     \item As a User, I want to get a Notification on my mobile about a new message.
     \item As a User, I want to reply to a message I'm reading.
     \item As a User, I want to write a text message for a specific thread.
     \item As a User, I want to read a message from a specific thread. 
   \end{itemize}
\section{Current state}

\section{Next steps}

\chapter{Technical basics}

\section{Beap and BeapDB}

\section{Android}

\section{Permissions and user types}

\chapter{Blubb android app}

\section{Architecture overview}

\section{Communication with Beap}

\section{Sqlite as a local database}

\section{Singleton classes}

\subsection{General matter}

\subsection{SessionManager}

\subsection{ThreadManager}

\subsection{MessageManager}

\section{User interface}

\subsection{Design}

\subsection{Activities}

\subsection{AsyncTasks}

\section{Notifications}

\subsection{Motivation}

\subsection{Service}

\section{Manifest}

\section{Gradle build}

\chapter{User documentation}

\section{Thread overview}

\subsection{Show Threads}

\subsection{Thread details}

\subsection{Create a new thread}

\subsection{Modify thread title and description}

\section{Thread messages}

\subsection{Show messages for a thread}

\subsection{Write a new message}

\subsection{Modify a message}

\subsection{Reply to a message}

\subsection{Read replies}

\section{Settings and login}

\subsection{login}

\subsection{logout}

\subsection{Reset the password}

\subsection{First login}

\subsection{Settings}

\subsection{Stay logged in}

\chapter{Valuation}

\chapter{Prospect blubb}


The second Section.\\

\end{document}
